### 2021-04-26 sections/working-papers.tex
Update working-papers.tex

\begin{benumerate}{4}

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. (2020).  Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study. {\itshape Tufte Working Papers}, (1), 1--15. {\footnotesize \scshape [in Spanish]}. {\scshape url:} \href{https://tuftepapers.com/2020/09/aplicacion-de-ForceAtlas2-algoritmo-de-diseno-grafico.html}{\textcolor{blue}{https://tuftepapers.com}}. {\scshape {\footnotesize SocArXiv} doi:} \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}

\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A. (2016). Revolving Door. Analysis of Public-Private Circulation in Chile (2000-2014). {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, (7), 1--40. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Soto, D. (2016). Pluralism in the Chilean Digital Mass Media, Exploratory Study of Key Cases. {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, (2), 1--26. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}
\end{benumerate}

>>>>

\begin{benumerate}{5}

\item{\small Gonz\'alez-Bustamante, B. (2021, {\itshape forthcoming}). Sophistication, Participation, and Political Engagement in Latin America. {\itshape Tufte Working Papers}, 2. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/r4pj8}{\textcolor{blue}{10.31235/osf.io/r4pj8}}} \vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B., \& Cisternas, C. (2020).  Applying ForceAtlas2, a Continuous Graph Layout Algorithm, to the Elites Study. {\itshape Tufte Working Papers}, 1, 1--15. {\footnotesize \scshape [in Spanish]}. {\scshape \footnotesize SocArXiv}: \href{https://doi.org/10.31235/osf.io/gxrkc}{\textcolor{blue}{10.31235/osf.io/gxrkc}}} \vspace{1mm}

\item{\small Maillet, A., Gonz\'alez-Bustamante, B., \& Olivares, A. (2016). Revolving Door. Analysis of Public-Private Circulation in Chile (2000-2014). {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}} \vspace{1mm}

@@

\item{\small Gonz\'alez-Bustamante, B., \& Soto, D. (2016). Pluralism in the Chilean Digital Mass Media, Exploratory Study of Key Cases. {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26. {\footnotesize \scshape [in Spanish]}. {\scshape doi}: \href{http://doi.org/10.13140/RG.2.2.33899.03362}{\textcolor{blue}{10.13140/RG.2.2.33899.03362}}}
\end{benumerate}
